---
output: 
pdf_document:
citation_package: natbib
keep_tex: false
fig_caption: true
latex_engine: pdflatex
title: scoping review summary
author:
- name: Sangeeta Bhatia
affiliation: Imperial College London
abstract: 
keywords: 
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: 
biblio-style: apsr
endnote: no
---

```{r setup, eval = TRUE}
africa <- readRDS("africa_iso3c.rds")
ds_types <- read_csv("study_ds_types.csv")
x <- count(ds_types, data_category)
emp <- x$n[x$data_category == "empirical"]
est <- x$n[x$data_category != "empirical"]
empc <- unique(ds_types$country[ds_types$data_category == "empirical"])
missing <- paste(africa[! africa %in% empc], collapse = " ")
```

Across
the 30 studies, we identified `r emp` empirical human mobility data sets
and `r est` mobility proxies. 

Empirical data were available for `r length(empc)` countries on the African
mainland.

Empirical data were not available for `r missing`.

```{r}
gbmd <- ds_types[ds_types$datasource_type == "GBMD", ]
gbmd <- unique(gbmd$country)

unhcr <- ds_types[ds_types$datasource_type == "unhcr", ]
unhcr <- unique(unhcr$country)

x <- unique(c(gbmd, unhcr))
missing <- paste(africa[! africa %in% x], collapse = " ")
```

Data on long-term
migration patterns between countries was available, from GBMD (n = `r length(gbmd)`
countries) or data on refugee movement from UNHCR (n = `r length(unhcr)`)

```{r}
```
