---
output: 
pdf_document:
citation_package: natbib
keep_tex: false
fig_caption: true
latex_engine: pdflatex
title: scoping review summary
author:
- name: Sangeeta Bhatia
affiliation: Imperial College London
abstract: 
keywords: 
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: 
biblio-style: apsr
endnote: no
---

```{r setup, eval = TRUE}
africa <- readRDS("africa_iso3c.rds")
ds_types <- read_csv("study_ds_types.csv")
x <- count(ds_types, data_category)
emp <- x$n[x$data_category == "empirical"]
est <- x$n[x$data_category != "empirical"]
empc <- unique(ds_types$country[ds_types$data_category == "empirical"])
missing <- paste(africa[! africa %in% empc], collapse = " ")
```

Across
the 30 studies, we identified `r emp` empirical human mobility data sets
and `r est` mobility proxies. 

Empirical data were available for `r length(empc)` countries on the African
mainland.

Empirical data were not available for `r missing`.

```{r}
gbmd <- ds_types[ds_types$datasource_type == "GBMD", ]
gbmd <- unique(gbmd$country)

unhcr <- ds_types[ds_types$datasource_type == "unhcr", ]
unhcr <- unique(unhcr$country)

x <- unique(c(gbmd, unhcr))
missing <- paste(africa[! africa %in% x], collapse = " ")
```

Data on long-term
migration patterns between countries was available, from GBMD (n = `r length(gbmd)`
countries) or data on refugee movement from UNHCR (n = `r length(unhcr)`)

```{r}
emp <- ds_types[ds_types$data_category == "empirical", ]
not_adm0 <- emp[emp$data_spatial_resolution != "adm0", ]
x <- length(unique(not_adm0$country))
```

Out of 54 countries, we found only `r x` with subnational mobility data.

```{r}
census <- not_adm0[not_adm0$datasource_type %in% c("census", "ipums", "hdss"), ]
x <- length(unique(census$country))

cdr <- not_adm0[not_adm0$datasource_type %in% "cdr", ]
y <- unique(cdr$country)

sm <- not_adm0[not_adm0$datasource_type %in% "social_media", ]
z <- unique(sm$country)

intv <- not_adm0[not_adm0$datasource_type %in% "interview", ]
zpr <- unique(intv$country)


```
These were informed by census (n = `r x` countries), mobile phone records
(CDR, n = `r length(y)`, `r paste(y, collapse = " ")`), 
social media records (n = `r length(z)`, CHECK?) [49] or dedicated
surveys (n = `r length(zpr)`).

```{r}
est <- readr::read_csv("estimated_data_locations_scale.csv")
not_adm0 <- est[est$scale != "ADM0", ]
x <- length(unique(not_adm0$country))
```
Overall, we have subnational mobility proxies for `r x` countries. We
will now exclude those derived from non-African countries.

```{r}
## Exclude huang as they are based on non-African data
not_adm0 <- not_adm0[not_adm0$bibkey != "huang2013open", ]
x <- length(unique(not_adm0$country))
emp_not_adm0 <- emp[emp$data_spatial_resolution != "adm0", ]
y <- length(unique(africa[! africa %in% emp_not_adm0$country]))
```
The empirical data described above was used to derive subnational
mobility proxies for `r x` countries in Africa, `r y` of which had no
empirical data informing subnational mobility.

```{r}
x <- read_csv("estimated_data_locations_scale.csv")
air_vol <- x[x$bibkey == "huang2013open", ]
```
Some used airline passenger volume from Europe, United States, and
Canada to inform mobility proxies in `r length(unique(air_vol$location))` cities across 
`r length(unique(air_vol$country))` countries in Africa.

```{r}
x <- count(emp, data_available)
yes <- x$n[x$data_available == "yes"]
est <- ds_types[ds_types$data_category != "empirical", ]
y <- count(est, data_available)
est_yes <- y$n[y$data_available == "yes"] 
```
In studies that used empirical data sources to calibrate mobility
models, the underlying data were rarely shared with the publication,
even when commercial re- strictions did not prevent data sharing
(`r yes` empirical data sets readily available). Mobility proxies were
more often available `r est_yes`.

